paper3

### 2022-08-19 paper3.Rmd
grid

## Download the visual and sensory aspect of the LANDMAP data  
VS <- read_sf("http://lle.gov.wales/catalogue/item/LandmapVisualSensory.json") %>%
  st_make_valid() %>%
  mutate(ScenicQuality = factor(VS_46, levels = c("Low", "Moderate", "High", "Outstanding")),
             Integrity = factor(VS_47, levels = c("Low", "Moderate", "High", "Outstanding")),
             Character = factor(VS_48, levels = c("Low", "Moderate", "High", "Outstanding")),
                Rarity = factor(VS_49, levels = c("Low", "Moderate", "High", "Outstanding")))

## Download Scenic-Or-Not data
sc <- read_tsv("http://scenicornot.datasciencelab.co.uk/votes.tsv",
               col_types = cols("ID" = col_number(),
                                "Lat" = col_double(),
                                "Lon" = col_double(),
                                "Average" = col_double(),
                                "Variance" = col_double(),
                                "Votes" = col_character(),
                                "Geograph URI" = col_character())) %>%
  rowwise() %>%
  mutate(Mean = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Median = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Variance = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% var(),
         Entropy = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         BayeScore = Votes %>% BayesRank(K = 10, α = .05))%>%
  st_as_sf(coords = c("Lon","Lat"), crs = 4326) %>%
  st_transform(crs = 27700)
```

```{r}
LANDMAP <- sc %>% 
  st_join(VS, .) %>% 
  aggregate(Votes~UID, data = ., paste0, collapse = ",") %>%
  merge(VS, ., by = "UID", all = T) %>%
  as_tibble() %>% 
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Scenicness.entropy_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         Scenicness.number_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% na.omit() %>% length()) %>%
  ungroup()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Median~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_median = Median %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_median = Median %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median()) %>%
  ungroup()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Mean~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median()) %>%
  ungroup()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(BayeScore~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_bayescore = BayeScore %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_bayescore = BayeScore %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Consultant = ifelse(str_detect(VS_1a, "Bronwen Thomas"), "B", "A")) %>%
  ungroup()

plot(LANDMAP["ScenicQuality"], border = 'NA', col = RColorBrewer::brewer.pal(4, "YlOrBr"), key.pos = 1)  
```

@@

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., 
                fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), 
                quantiles = c(0.25, 0.75)) %>%
  mutate(Wildness.iqr = q75 - q25) %>%
  bind_cols(LANDMAP, .) %>%
  dplyr::select(UID, CLS_1, CLS_2, CLS_3, CLS_4, ScenicQuality, Consultant,
                Votes, Scenicness.mean_of_all, Scenicness.median_of_all,
                Scenicness.entropy_of_all, Scenicness.number_of_all,
                Scenicness.mean_of_median, Scenicness.median_of_median,
                Scenicness.mean_of_mean, Scenicness.median_of_mean,
                Scenicness.mean_of_bayescore, Scenicness.median_of_bayescore,
                Wildness.mean = mean, Wildness.median = median, Wildness.iqr, 
                Wildness.cv = coefficient_of_variation, Wildness.variance = variance) %>%
  st_transform(crs = 27700)

landmap <- st_cast(LANDMAP, "POLYGON") %>%
  dplyr::mutate(x = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 1],
                y = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 2])
summary(landmap)
```

@@

# reticulate::py_config() # why numpy_version couldn't be found?
# use_python("Z:\\R\\R projects\\LCA-GB\\my_env_Python_3.9.13\\Scripts\\python.exe")
# 
# # use_virtualenv("Z:\\R\\R projects\\LCA-GB\\my_env_Python_3.9.13", required = TRUE)
# 
# install.packages("usethis")
# usethis::edit_r_environ()
# usethis::edit_r_profile()
```

```{python}
import geopandas as gpd
import pandas as pd
from sklearn.preprocessing import OrdinalEncoder
from sklearn.compose import make_column_transformer

landmap = r.landmap
landmap = landmap.dropna(subset=['ScenicQuality'])

print(landmap)
landmap.describe()
print(landmap['ScenicQuality'].value_counts())

landmap.isnull().sum()

landmap_A = landmap.query("Consultant in ['A']")
landmap_B = landmap.query("Consultant in ['B']")

print(landmap.shape)
print(landmap_A.shape)
print(landmap_B.shape)

# def split_consultant(landmap):
#   X = landmap.loc[:, ['Scenicness.mean', 'Scenicness.entropy', 'Wildness.median', 'Wildness.iqr']]
#   y = landmap.loc[:, ['ScenicQuality']]
# 
#   # Instantiate the label encoder
#   transformer = make_column_transformer(
#     (OrdinalEncoder(categories=[['Low', 'Moderate', 'High', 'Outstanding']]), ['ScenicQuality'])
#   )
# 
#   y = transformer.fit_transform(y)
#   
#   y = pd.DataFrame(y, columns = ['ScenicQuality'])
#   return X, y
# 
# def EDA_plot(y, X):
#   import pandas as pd
#   # concatenating y and X along columns
#   landmap_concat = pd.DataFrame(pd.concat([y.reset_index(drop=True), X.reset_index(drop=True)], axis=1))
#   print(landmap_concat.shape)
# 
#   import seaborn as sns
#   sns.set()
#   sns.pairplot(landmap_concat, hue='ScenicQuality', palette='vlag', height=3)

# split train/test set
# X = landmap_B.loc[:, ['Scenicness.mean', 'Wildness.mean']]
X = landmap_B.loc[:, ['Scenicness.median_of_bayescore', 'Wildness.median', 'x', 'y']]
y = landmap_B.loc[:, ['ScenicQuality']]

# from sklearn.preprocessing import OrdinalEncoder
# OE = OrdinalEncoder()
# y[['Scale']] = OE.fit_transform(y[['ScenicQuality']])

scale_mapper = {'Low': int(0), 
                'Moderate': int(1), 
                'High': int(2), 
                'Outstanding': int(3)}

y[['ScenicQuality']] = y[['ScenicQuality']].replace(scale_mapper).astype('int')

# X, y = split_consultant(landmap)
print(y.shape, X.shape)
X.head()
y.head()
# EDA_plot(y, X)

# -- Create train/test split
from sklearn.model_selection import train_test_split
X_train, X_test, y_train, y_test = train_test_split(X, y, 
                                                    test_size = 0.2, 
                                                    random_state = 2046, 
                                                    stratify = y)
```

## Hyperparameter Tuning

@@

# Consultant B
params = {
          'booster': 'gbtree',
        'num_round': 1434, #1433.996,
              'eta': 0.892,
            'gamma': 0,
        'max_depth': 4,
 'min_child_weight': 0.6,
        'subsample': 0.500,
 'colsample_bytree': 1,
        'num_class': 4,
        'objective': 'multi:softmax',
      'eval_metric': 'merror',
             'seed': 1995
  }

@@

# model = xgb.train(space_eval(param_space, best_params),
#                   dtrain,
#                   num_boost_round = 500,
#                   evals = [(dtrain, 'train'), (dtest, 'test')],
#                   early_stopping_rounds = 250)

model = xgb.train(params,
                  dtrain,
                  num_boost_round = 500,
                  evals = [(dtrain, 'train'), (dtest, 'test')],
                  verbose_eval = 100,
                  early_stopping_rounds = 251)

@@

y_pred = model.predict(dtest)

# -- evaluate model using test data
from sklearn.metrics import accuracy_score

accuracy = accuracy_score(y_test, y_pred)
print("Accuracy: %.2f%%" % (accuracy * 100.0))

from sklearn.metrics import cohen_kappa_score
kappa = cohen_kappa_score(y_pred, y_test)
print("Kappa: %.2f" % (kappa))

# -- save to JSON
model.save_model("Z:\\R\\R projects\\LCA-GB\\models\\model_B.json")
```

@@

```{python, engine.path = '.venv/Scripts/python'}
import shap
import numpy as np
import matplotlib.pyplot as plt
import matplotlib.pylab as pl
import xgboost as xgb
from sklearn.preprocessing import StandardScaler
from sklearn.metrics import plot_confusion_matrix

@@

# -- load the saved model
model = xgb.XGBClassifier()
model.load_model("Z:\\R\\R projects\\LCA-GB\\models\\model_B.json")
```

## Confusion matrix
```{python}
# -- view the confusion matrix
class_names = ['Low', 'Moderate', 'High', 'Outstanding']
disp = ConfusionMatrixDisplay.from_predictions(model, X_test, y_test, 
                             display_labels = class_names, 
                             cmap = plt.cm.Blues, 
                             xticks_rotation = 'vertical')
```

```{python}
# -- play shap
explainer = shap.TreeExplainer(model)
shap_values = explainer.shap_values(X_train, approximate=True)

shap.plots.beeswarm(shap_values, show=False, color_bar=False)
plt.colorbar()
plt.show()

# shap.summary_plot(shap_values[1], 
#                   X_train.values, 
#                   feature_names = X_train.columns,
#                   plot_size = (10, 4))
#                   
# plt.gcf().axes[-1].set_aspect('auto')
# plt.tight_layout()
# As mentioned, smaller "box_aspect" value to make colorbar thicker
# plt.gcf().axes[-1].set_box_aspect(200)

@@

>>>>

## Download the visual and sensory aspect of the LANDMAP data  
VS <- read_sf("http://lle.gov.wales/catalogue/item/LandmapVisualSensory.json") %>%
  st_make_valid() %>%
  mutate(ScenicQuality = factor(VS_46, levels = c("Low", "Moderate", "High", "Outstanding")),
         Consultant = ifelse(str_detect(VS_1a, "Bronwen Thomas"), "B", "A")) %>%
             # Integrity = factor(VS_47, levels = c("Low", "Moderate", "High", "Outstanding")),
             # Character = factor(VS_48, levels = c("Low", "Moderate", "High", "Outstanding")),
             #    Rarity = factor(VS_49, levels = c("Low", "Moderate", "High", "Outstanding"))) %>%
  dplyr::select(UID, CLS_1, CLS_2, CLS_3, CLS_4, Consultant, ScenicQuality)

## Download Scenic-Or-Not data
sc <- read_tsv("http://scenicornot.datasciencelab.co.uk/votes.tsv",
               col_types = cols("ID" = col_number(),
                                "Lat" = col_double(),
                                "Lon" = col_double(),
                                "Average" = col_double(),
                                "Variance" = col_double(),
                                "Votes" = col_character(),
                                "Geograph URI" = col_character())) %>%
  rowwise() %>%
  mutate(Mean = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Median = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Variance = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% var(),
         Entropy = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         BayeScore = Votes %>% BayesRank(K = 10, α = .05),
         Number = Votes %>% strsplit(",") %>% unlist() %>% length())%>%
  st_as_sf(coords = c("Lon","Lat"), crs = 4326) %>%
  st_transform(crs = 27700)
```

```{r}
LANDMAP <- sc %>% 
  st_join(VS, .) %>%
  aggregate(Votes~UID, data = ., paste0, collapse = ",") %>%
  merge(VS, ., by = "UID", all = T) %>%
  as_tibble() %>% 
  rowwise() %>%
  mutate(Scenicness.number_of_all = strsplit(Votes, ",") %>% unlist() %>% na.omit() %>% length(),
         Scenicness.mean_of_all = strsplit(Votes, ",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_all = strsplit(Votes, ",") %>% unlist() %>% as.numeric() %>% median(),
         Scenicness.entropy_of_all = strsplit(Votes, ",") %>% unlist() %>% as.numeric() %>% entropy()) %>%
  ungroup() %>%
  st_as_sf()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Median~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_median = strsplit(Median, ",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_median = strsplit(Median, ",") %>% unlist() %>% as.numeric() %>% median()) %>%
  dplyr::select(-Median) %>%
  ungroup() %>%
  st_as_sf()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Mean~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_mean = strsplit(Mean, ",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_mean = strsplit(Mean, ",") %>% unlist() %>% as.numeric() %>% median()) %>%
  dplyr::select(-Mean) %>%
  ungroup() %>%
  st_as_sf()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(cbind(BayeScore, Number, VR = BayeScore*Number)~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_bayescore = strsplit(BayeScore, ",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_bayescore = strsplit(BayeScore, ",") %>% unlist() %>% as.numeric() %>% median(),
         Score_multiplied_by_Number = strsplit(VR, ",") %>% unlist() %>% as.numeric() %>% sum(na.rm = TRUE),
         Scenicness.weighted_bayescore =  Score_multiplied_by_Number/(Scenicness.number_of_all + 3) + 
                                          3*Scenicness.mean_of_bayescore/(Scenicness.number_of_all + 3)) %>%
  dplyr::select(-c(BayeScore, Number, VR, Score_multiplied_by_Number)) %>%
  ungroup() %>%
  st_as_sf()

# plot(LANDMAP["ScenicQuality"], border = 'NA', col = RColorBrewer::brewer.pal(4, "YlOrBr"), key.pos = 1)  
```

@@

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., 
                fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), 
                quantiles = c(0.25, 0.75)) %>%
  mutate(Wildness.mean = mean,
         Wildness.median = median,
         Wildness.iqr = q75 - q25,
         Wildness.cv = coefficient_of_variation,
         Wildness.variance = variance) %>%
  dplyr::select(-c(mean, median, q25, q75, coefficient_of_variation, variance)) %>%
  bind_cols(LANDMAP, .) %>%
  st_transform(crs = 27700)

landmap <- st_cast(LANDMAP, "POLYGON") %>%
  dplyr::mutate(UID = row_number(),
                x_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 1],
                y_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 2])
summary(landmap)
```

Separate the consultant and then split train-test sets
```{r}
landmap_A = landmap %>% filter(Consultant == "A")
landmap_B = landmap %>% filter(Consultant == "B")

library(rsample)

# Set the random number stream using `set.seed()` so that the results can be 
# reproduced later. 
set.seed(2046)

# Save the split information for an 80/20 split of the data
split <- landmap %>% 
  filter(!is.na(ScenicQuality)) %>% 
  initial_split(prop = 0.80, strata = ScenicQuality)

train_set <- training(split) %>% st_drop_geometry() 
 test_set <- testing(split) %>% st_drop_geometry() 
dim(train_set)
dim(test_set)

X_train <- train_set %>% 
  dplyr::select(Scenicness = Scenicness.median_of_bayescore,
                Wildness = Wildness.median, x_coord, y_coord)
 X_test <-  test_set %>% 
   dplyr::select(Scenicness = Scenicness.median_of_bayescore,
                 Wildness = Wildness.median, x_coord, y_coord)

y_train <- train_set %>% dplyr::select(ScenicQuality)
 y_test <-  test_set %>% dplyr::select(ScenicQuality)  
```

@@

# reticulate::py_config() # why numpy_version couldn't be found?
# use_python("Z:\\R\\R projects\\LCA-GB\\my_env_Python_3.9.13\\Scripts\\python.exe")
# 
# # use_virtualenv("Z:\\R\\R projects\\LCA-GB\\my_env_Python_3.9.13", required = TRUE)
# 
# install.packages("usethis")
# usethis::edit_r_environ()
# usethis::edit_r_profile()
```
```{python}
# -- load in the train/test sets
X_train = r.X_train
y_train = r.y_train
 X_test = r.X_test
 y_test = r.y_test

scale_mapper = {'Low': int(0),
                'Moderate': int(1),
                'High': int(2),
                'Outstanding': int(3)}
y_train[['ScenicQuality']] = y_train[['ScenicQuality']].replace(scale_mapper).astype('int')
 y_test[['ScenicQuality']] = y_test[['ScenicQuality']].replace(scale_mapper).astype('int')
```
## Hyperparameter Tuning

@@

# Consultant B
params = {'booster': 'gbtree',
        'num_round': 1434, #1433.996,
              'eta': 0.892,
            'gamma': 0,
        'max_depth': 4,
 'min_child_weight': 0.6,
        'subsample': 0.500,
 'colsample_bytree': 1,
        'num_class': 4,
        'objective': 'multi:softmax',
      'eval_metric': 'merror',
             'seed': 1995}

@@

model = xgb.train(space_eval(param_space, best_params),
                  dtrain,
                  num_boost_round = 500,
                  evals = [(dtrain, 'train'), (dtest, 'test')],
                  early_stopping_rounds = 250)

# model = xgb.train(params,
#                   dtrain,
#                   num_boost_round = 500,
#                   evals = [(dtrain, 'train'), (dtest, 'test')],
#                   verbose_eval = 100,
#                   early_stopping_rounds = 251)

@@

y_pred = model.predict(dtest)
y_pred = y_pred.astype(int)
y_true = y_test.values.flatten()

# -- evaluate model using test data
# -- overall accuracy
from sklearn.metrics import accuracy_score
y_actual = y_test.values.flatten()
accuracy = accuracy_score(y_true, y_pred)
print("Accuracy: %.2f%%" % (accuracy * 100.0))

# -- Cohen's kappa 
from sklearn.metrics import cohen_kappa_score
kappa = cohen_kappa_score(y_true, y_pred)
print("Kappa: %.2f" % (kappa))

# -- save to JSON
model.save_model("Z:\\R\\R projects\\LCA-GB\\models\\model.json")
```

@@

```{python, engine.path = '.venv/Scripts/python'}
import shap
import numpy as np
import matplotlib.pyplot as plt
import matplotlib.pylab as pl
import xgboost as xgb
from sklearn.preprocessing import StandardScaler

@@

# -- load the saved model
model = xgb.XGBClassifier()
model.load_model("Z:\\R\\R projects\\LCA-GB\\models\\model.json")
```

## Confusion matrix and its visualisation
```{python}
from sklearn.metrics import confusion_matrix, ConfusionMatrixDisplay
import matplotlib.pyplot as plt

cm = confusion_matrix(y_test.values, y_pred)
# -- view the confusion matrix
disp = ConfusionMatrixDisplay(confusion_matrix = cm, 
                              display_labels = ['Low', 'Moderate', 'High', 'Outstanding'])
disp.plot(cmap = plt.cm.Blues)
plt.show(); plt.close()
```

```{python plot}
X =  r.landmap.loc[:, ['Scenicness.median_of_bayescore', 'Wildness.median', 'x', 'y']]
# -- play shap
explainer = shap.TreeExplainer(model)
# X = landmap.loc[:, ['UID', 'Scenicness.median_of_bayescore', 'Wildness.median', 'x', 'y']]
# The approximate argument set to True to fix some of the shap_values with NaN value
# shape of shap_values is : (4, 1321, 4) means 4 classes, 1321 rows(observations), each 4 columns(features).
shap_values = explainer.shap_values(X, approximate = True)

# shap.plots.beeswarm(shap_values, show = True, color_bar = False)
# plt.colorbar()
# plt.show()

# In the case of matplotlib version 3.5 above, the adjustment of colorbar legend was referred to https://github.com/slundberg/shap/issues/2493
# summary plot for "CLASS 0" (Low scenic quality) 
shap.summary_plot(shap_values[0],
                  X_train.values,
                  feature_names = ['Scenicness', 'Wildness', 'x_coord', 'y_coord'], #X_train.columns,
                  show = False,
                  # plot_type = 'compact_dot', # making the dots disappear
                  plot_size = (50, 6))
plt.gcf().axes[-1].set_aspect('auto')
plt.tight_layout()
plt.gcf().axes[-1].set_box_aspect(40) # smaller "box_aspect" value to make colorbar thicker
plt.show(); plt.close()
# plt.savefig('fig_tes1.png', bbox_inches='tight',dpi=300); plt.close()

# X_names = ['pct_18_34','pct_white','pct_bach',
#           'pct_no_car','log_pop_den','job_entropy','network_den',
#           'ave_trip_dist','pct_share','x_coord','y_coord']
# 
# fig, ax = plt.subplots(figsize=(8, 6),dpi=160)
# 
# shap.summary_plot(shap_interaction_values, X_coords, max_display=15, 
#                   feature_names = X_names,
#                   plot_type="compact_dot")
```
## Spatial patterns of SHAP values
```{python}
# landmap = r.landmap
X_vars = ['Scenicness','Wildness', 'x', 'y']

fig, ax = plt.subplots(2,2,figsize=(15,15))

for j in range(len(X_vars)):
  j = 1
    ax = ax.ravel()
    X.plot(ax=ax[j],column = shap_values.values[:,j],legend=True,
                 vmin=-0.8,vmax=0.8,cmap=shap.plots.colors.red_white_blue)

    ax[j].set_title("SHAP for\n" + X_vars[j],fontsize=10)

#fig.delaxes(ax[-1])

@@

```{r}
shap_values = py$shap_values
shap_Low = data.frame(shap_values[[1]]) %>% transmute(SHAP_Scenicness_Low = X1, 
                                                      SHAP_Wildness_Low = X2,
                                                      SHAP_Location_Low = X3 + X4) 
shap_Moderate = data.frame(shap_values[[2]]) %>% transmute(SHAP_Scenicness_Moderate = X1,
                                                           SHAP_Wildness_Moderate = X2,
                                                           SHAP_Location_Moderate= X3 + X4)
shap_High = data.frame(shap_values[[3]]) %>% transmute(SHAP_Scenicness_High = X1,
                                                       SHAP_Wildness_High = X2,
                                                       SHAP_Location_High = X3 + X4)
shap_Outstanding = data.frame(shap_values[[4]]) %>% transmute(SHAP_Scenicness_Outstanding = X1,
                                                              SHAP_Wildness_Outstanding = X2,
                                                              SHAP_Location_Outstanding = X3 + X4)

landmap_shap = cbind(landmap, shap_Low, shap_Moderate, shap_High, shap_Outstanding)
rm(list = c('shap_Low', 'shap_Moderate', 'shap_High', 'shap_Outstanding'))

```
## Visualising the spatial distributions of SHAP values for each covariate with each class
```{r}
library(ggplot2)

theme_map <- function(...) {
  theme_minimal() +
    theme(
      text = element_text(color = "#22211d"), # family = "Garamond", "Ubuntu Regular"
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      # panel.grid.minor = element_line(color = "#ebebe5", size = 0.2),
      panel.grid.major = element_blank(), #element_line(color = "#ebebe5", size = 0.2),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA), 
      panel.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA), 
      legend.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA),
      panel.border = element_blank(),
      ...
    )
}

f <- list()

for (i in 1:12) {
  f[[i]] <- ggplot() +
    geom_sf(data = landmap_shap, aes(fill = !!sym(names(landmap_shap)[i+25])), colour = NA) +
    theme_map() +
    labs(x = NULL, 
         y = NULL, 
         title = names(landmap_shap)[i+25]) + # stringr::str_c("SHAP for ", collapse = " ")
    theme(legend.position = "bottom",
          title = element_text(size = 15)) +
    scale_fill_gradient2(low = ("#CB181D"),
                         mid = "white",
                         name = NULL,
                         high = ("#2171B5"),
                         midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))
}

## -- multiplot function
multiplot <- function(plot.list, file, cols=3, layout=NULL) {
	library(grid)
	numPlots = length(plot.list)
	if (is.null(layout)) {
		layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
						ncol = cols, nrow = ceiling(numPlots/cols))
	}
	if (numPlots==1) {
		print(plots[[1]])
	} else {
	  grid.newpage()
	  pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
	  for (i in 1:numPlots) {
	  	matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
	  	print(plot.list[[i]], vp = viewport(layout.pos.row = matchidx$row,
	  									layout.pos.col = matchidx$col))
	  }
	}
}

## map together
setwd("Z:\\R\\R projects\\LCA-GB\\figures")
png(filename = "SHAP_values.png", w = 10*2, h = 6*2, units = "in", res = 300)
par(mar = c(0,0,0,0))
multiplot(list(f[1], f[2], f[3], f[4], 
               f[5], f[6], f[7], f[8], 
               f[9], f[10], f[11], f[12]), cols = 4)
dev.off()
```
